Comparison and Evaluation of Popular Syntax Highlighting Themes in Terms of Color Correlated Temperature Values

### 2022-04-25 doc/manuscript.tex
.

In this study, the CCT was utilized to calculate the quantity of blue light contained in popular color themes chosen by developers. It was observed that the average CCT values of both the dark and light versions of the examined themes were above the D65 threshold and contained intense blue light. Theme developers should consider the risks that blue light poses to human eye health while creating their themes.

The amount of blue light in the color theme was determined using the workflow shown in Figure
\ref{fig:general-flowchart}. Primarily, the themes to be used in the study were selected.

@@

Among the many monospace fonts, the study was carried out only with a font installed on the system and available as a default. As explained in the \ref{sec:material-methods.inputs.editor} section, colored codes are obtained with the VS Code programming editor on the Windows 10 operating system.
During the research, the Consolas\cite{microsoft2022consolas} fixed-width TrueType font, displayed in Figure \ref{fig:consolas} by default in this environment, is also used as a default 14-point size. Since it is predefined, this font selection is considered to reflect the common situation experienced by developers.

@@

\begin{figure}[h]
  \centering
  \includesvg[inkscapelatex=false, width=400pt]{code.svg}
  \caption{Colored code}
  \label{fig:code}
\end{figure}

\begin{figure}[H]
  \centering
  \includesvg[inkscapelatex=false, width=200pt]{string.svg}
  \caption{Colored code content as a single string}
  \label{fig:string}
\end{figure}

>>>>

Bu çalışmada seçilen bir örnek kaynak kod, belirli ölçütler dikkate alınarak belirlenen popüler renklendirme temalarının
her biriyle renklendirilmiş ve elde edilen içeriklerin ortalama CCT değerleri hesaplanarak karşılaştırılmıştır.
Araştırma kapsamında izlenen iş akışı Şekil \ref{fig:general-flowchart}'de görülmektedir. İzlenen yöntemin temelinde,
renklendirilmiş kaynak kod içeriğinin ilk karakterden son karaktere kadar ilerleyen tek bir karakter dizisi olarak ele
alınması yatmaktadır. Bu dizi içinde her bir karakter seçilen yazıtipinden hareketle üretilen bir bit eşlem "karakter
kutusu" olarak yorumlanmıştır. Her bir karakter kutusu tema tarafından tanımlanan ön plan ve arka plan renkleriyle
renklendirilmiş piksellerden oluşmaktadır. Arka plan ve ön plan renkleri kapsadığı piksel alanları oranında o karakter
kutusunun ortalama CCT değerine ve her bir karakter kutusu da o kutunun sıklığı oranında içeriğin tamamına ait ortalama
CCT değerine katkıda bulunmaktadır. "Correlated Colored Code Temperature" (CCCT) olarak adlandırdığımız bu ortalama CCT
değeri yüksek hassasiyete sahip olan mutlak bir değer olmaktan ziyade ilgili tema renkleriyle kaynak kodun bir bütün
halde sahip olacağı ortalama CCT değeri hakkında bir yaklaşıklıklığı temsil etmektedir. Bu şekilde temaya özgü
olarak belirlenen CCCT değerleriyle kod renklendirme temalarının karşılaştırılması için yeni bir nicel ölçüt ortaya
konulmuştur.

Çalışma kapsamında geliştirilen tüm çözümleme programları ve üretilen veriler bir Github kod deposunda açık kaynak halde 
sunulmuştur\cite{ccct2022github}. Rationales behind all the selections in the analysis were explained in further sections.

\begin{comment}
In this study, the CCT was utilized to calculate the quantity of blue light contained in popular color themes chosen by developers. It was observed that the average CCT values of both the dark and light versions of the examined themes were above the D65 threshold and contained intense blue light. Theme developers should consider the risks that blue light poses to human eye health while creating their themes.

The amount of blue light in the color theme was determined using the workflow shown in Figure
\ref{fig:general-flowchart}. Primarily, the themes to be used in the study were selected.
\end{comment}

@@

Among the many monospace fonts, the study was carried out only with a font installed on the system and available as a
default. As explained in the \ref{sec:material-methods.inputs.editor} section, colored codes are obtained with the VS
Code programming editor on the Windows 10 operating system. During the research, the
Consolas\cite{microsoft2022consolas} fixed-width TrueType font, displayed in Figure \ref{fig:consolas} by default in
this environment, is also used as a default 14 pixel size. Since it is predefined, this font selection is considered to
reflect the common situation experienced by developers.

@@

\begin{figure}[h]
  \centering
  \includesvg[inkscapelatex=false, width=370pt]{code.svg}
  \caption{Colored code}
  \label{fig:code}
\end{figure}
